Simulation Study: Null Dependent Covariate (cubic)

### 2019-04-16 datasets/simulations/nulldependent/simulations-nulldependent-cubic.Rmd
Fix typo in null dep Rmd

```{r strong-one-simulation}
onerun <- simNullDependent(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                           icovariate = icovariate, null_dist = null_dist, null_inv = null_inv,
                           null_dependence = 0.3, execute = FALSE)
```

>>>>

```{r strong-one-simulation}
onerun <- simNullDependent(bdplus, m = m, pi0 = pi0, es_dist = es_dist, ts_dist = ts_dist,
                           icovariate = icovariate, null_dist = null_dist, null_inv = null_inv,
                           null_dependence = 0.7, execute = FALSE)
```
